\speculake: Hiding Malware in Speculative Execution

### 2018-12-11 paper/payloads.tex
add missing cite

We can overcome this by having the trigger program communicate the decryption
key to the payload program via the branch predictor. While prior work has used
the branch predictor to exfiltrate keys from other sensitive
processes~\cite{lee2017inferring}, we inject a key into the speculating payload program
from the external trigger program. To do this, we use
multiple speculative entry points, each that derives a unique decryption key
before calling a common decryption
routine. Since the exact speculative entry point is determined by the trigger
program, an analyst cannot trivially discover the decryption key directly from the payload
program.

>>>>

We can overcome this by having the trigger program communicate the decryption
key to the payload program via the branch predictor. While prior work has used
the branch predictor to exfiltrate keys from other sensitive
processes~\cite{aciiccmez2007predicting}, we inject a key into the speculating payload program
from the external trigger program. To do this, we use
multiple speculative entry points, each that derives a unique decryption key
before calling a common decryption
routine. Since the exact speculative entry point is determined by the trigger
program, an analyst cannot trivially discover the decryption key directly from the payload
program.
